\mytitile\\~

### 2019-11-03 document.tex
Results 1st pass done

Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr1}+\hat H_{tr2}+\hat H_{dr1}+\hat H_{dr2}+\hat H_{int},
\end{equation}
where $\hat H_{int} = J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms. In the following, we will also transform \eqref{eq:master} into the frame rotating with both drives by an operator
\begin{align}
&\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\label{eq:R}\\
&\hat H_R = \hat R^{\dagger}\hat H \hat R - i\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
\end{align}
After the transformation and application of RWA:
\begin{equation}
\begin{aligned}
	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_d^{(1,2)}-\omega_{(1,2)},\\
	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{-(\omega_d^1 - \omega_d^2)t}\right],\\
	\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\\ 
	\hat H_{dr}^2 &\rightarrow \frac{\Omega_2}{2}(\hat c  + \hat c^\dag).
\end{aligned}
\label{eq:RWA}
\end{equation}

@@

Remarkably, in areas I, II and III we could observe avoided crossings and triplet transitions which turn out to be impossible to explain using only the stationary Hamiltonian without driving terms. We confirm this by numerically diagonalizing $\hat H_{tr1}+\hat H_{tr2}+\hat H_{int}$ taking 3 levels for each transmon (and total 9 basis states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:statinary_levels} in Appendix. While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}, it completely misses the Roman-numbered effects. Taking into account more energy levels of each transmon does not help, and is not even necessary to reproduce this effect, as we will show in the following.

@@

\paragraph{Features I, II and III.} First, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the transmon 2. Upon this, it has become clear that feature II and feature III actually are of the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition from $\ket{00}$ to $\ket{01}$ intersects with the two-photon one $\ket{20/2}$ ($\ket{10}$ intersects $\ket{02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b) where the spectral lines are identified with the corresponding transitions.

From \autoref{fig:statinary_levels} we conclude that avoided crossing in III is between two transitions: $\ket{00}\rightarrow\ket{12/3}$ and $\ket{10}\rightarrow \ket{02}$ which are of the same frequency when $\omega_1 = \omega_2-\alpha_2/2$. The latter process is discernible in \autoref{fig:statinary_levels} as it depopulates $\ket{10}$, but is not visible in \autoref{fig:two-tone}. From additional simulations, we have found that the size of the splitting depends on the driving power on the first transmon; the results are shown in \autoref{fig:zoom}. There is no dependence on the drive power of the second transmon, though. As one can see, the growth of the splitting with increasing power is approximately linear: its width is roughly equal to the FWHM of the $\ket{10}$ spectral line which is approximately $\Omega_1/2\pi$ Hz.

@@

These observation lead to understanding that the effect is caused by light dressing. In case III, the first transmon is dressed by a strong resonant field; in case II, the second one; finally, in case I, both transmons are dressed at the same time. We will discuss these effects in greater detail in \autoref{sec:theory}.

@@

\begin{figure*}
	\centering
	\includegraphics[width=.9\linewidth]{main_scheme}
	\caption{Explaining the origin of the AT satellites for feature III. \textbf{(a)} System level structure at 3.65 mA. At this current, the first transmon (orange) is below the second one (blue) exactly by $\alpha_2/2$. The first transmon is driven by a strong signal of amplitude $\Omega_1$ at a small detuning $\Delta_1$ from $\omega_1$ shown in green. The transmon-transmon interaction in RWA conserves the number of excitations and is depicted as orange-blue circles. \textbf{(b)} Moving to the frame rotating with the drive of the first transmon, we make all the states $\ket{0j},\ket{1j}$ nearly degenerate (in fact, now the first transmon splitting equals $\Delta_1$). However, the presence of a strong excitation lifts the degeneracy and the splitting changes to $\Omega_1^R = (\Omega_1^2 + \Delta_1^2)^{\frac{1}{2}}$ (the first transmon becomes light-dressed). \textbf{(c)} Transitions in the light-dressed system when the second qubit is excited (level subspaces coupled by $\hat H_{dr}^2$ are shown with blue ellipses). In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted: the green transitions are not shifted in frequency, the red are red-shifted by $\Omega^R_1/2$ and the blue are blue-shifted by $\Omega^R_1/2$. However, as shown in the right part of the panel, without the transmon-transmon interaction the satellite transitions are forbidden due the selection rule: $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2 \ket{b, j+1} = 0$ since $\braket{a}{b} = 0$. When the coupling equals $J$, the dispersive approximation yields $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2\ket{b, j+1}\propto J^2$ and the satellites become visible. Remarkably, due to the two-photon nature of the transitions, the Autler-Townes splitting in this case will be just $\Omega_1^R$.}
	\label{fig:main_scheme}
\end{figure*}

@@

Since we had already connected the additional avoided crossings with light dressing, it was natural to expect the Autler-Townes effect to play a part. For a three-level system, the standard A-T effect is reviewed in Appendix \ref{sec:3-level-at}. However, in our case the situation is more complicated. We will first explain the feature III. Feature II is explained in the exactly same way. Feature I is of the same origin but is not discussed here in such detail.

First of all, during the spectroscopy we apply only a single microwave tone, and thus is has to be simultaneously the coupler tone and the probe tone to observe the A-T effect. This configuration is possible due to the resonance condition between the transmons at III: the light is resonant with $\ket{10}$ and detuned from $\ket{01}$; however, it is instead resonant with a two-photon transition $\ket{02/2}$ (the resonance condition is $\omega_1 = \omega_2+\alpha_2/2$). Since the two-photon Rabi frequency is much smaller than the single-photon $\Omega_2$, it is natural to view this two-photon excitation as the probing process which does not affect the level structure. In other words, in our case the A-T coupling operator is $\hat H_{dr}^1$ (strong), and the probing operator is $\hat H_{dr}^2$ (weak in the two-photon regime). Their separation in our case is not in frequency but in the Hilbert subspaces they act upon.

In \autoref{fig:main_scheme}, we elaborate on how exactly the A-T effect occurs for feature III. \autoref{fig:main_scheme}~(a) demonstrates the unmodified level structure of the SAM. Orange (blue) levels correspond to first (second) qubit excited, the other being in the ground state. Orange ellipses denote the driving (detuned by $\Delta_1$ from $\omega_1$) of the first transmon. Note that it acts upon every pair of states $\ket{0j},\,\ket{1j},\ j=0..2$. The off-resonant two-photon drive on the second qubit is not shown here. Since from numerical simulation we know that level $\ket{02}$ is not necessary to observe the splitting, it is only shown with a dashed line. From here, we consider the first transmon to be a two-level qubit: $\ket{22}$ is not shown, $\hat H_{int}$ in RWA couples only $\ket{01},\,\ket{10}$ and $\ket{11},\,\ket{12}$.

The next step is to view the system in the frame rotating with the first transmon (\autoref{fig:main_scheme}~(b)). Just as in Appendix \ref{sec:3-level-at}, after rediagonalization it may be regarded as dressed by light, and the whole level system rearranges. Now, the first transmon splitting equals $\Omega_{1}^R = \sqrt{\Omega_1^2+\Delta_1^2}$, and its the new eigenstates (dressed states) are $\ket{a}$ and $\ket{b}$. The second transmon energies stay the same, and thus in overall we obtain just three doublets.

Mathematically, this procedure looks as follows. In the calculation below, we will use the following rotation operator (different from \eqref{eq:R}) to move to the rotating frame with \eqref{eq:rotation}:
\begin{equation}
R = \exp[-i\omega_d^1 t (b^{\dagger}b+c^{\dagger}c)]
\end{equation}

Note that for brevity reasons we rotate both transmon subspaces simultaneously (in contrast to what is shown in \autoref{fig:main_scheme}). Moreover, we consider a general case when $\omega_d^1 - \omega_d^2 = \delta \neq 0 $ and $\Delta_{1,2} = \omega_d^1-\omega_{1,2}$ and $\omega_1 - \omega_2$ not necessary equals $\alpha_2/2$. The resulting Hamiltonian with RWA:

\renewcommand{\kbldelim}{[}% Left delimiter
\renewcommand{\kbrdelim}{]}% Right delimiter
\begin{widetext}
	\begin{equation}\label{matrix} 
	\text{$H^R$} = \kbordermatrix{
		&\ket{00} & \ket{10} & \ket{01} & \ket{11} & \ket{02} & \ket{12} \\
		\ket{00}& 0 & \text{$\Omega_1/2 $} & \text{$\Omega _2$} e^{i \text{$\delta$} t}/2 & 0 & 0 & 0 \\
		\ket{10} & \text{$\Omega_1/2 $} & \text{$-\Delta_1 $} & J & \text{$\Omega_2$} e^{i \text{$\delta$} t}/2 & 0 & 0 \\
		\ket{01} & \text{$\Omega_2$} e^{-i \text{$\delta$} t}/2 & J & -\text{$\Delta_2 $} &
		\text{$\Omega_1$/2} & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta$} t}/2 & 0 \\
		\ket{11} & 0 & \text{$\Omega_2$} e^{-i \text{$\delta $} t}/2 & \text{$\Omega_1/2$} &
		\text{$-\Delta_2 -\Delta_1$} & \sqrt{2} J & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta
				$} t}/2 \\
		\ket{02} & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta$} t}/2 & \sqrt{2} J &
		\text{$\alpha$}-2 \text{$\Delta_2$} & \text{$\Omega_1/2$} \\
		\ket{12} & 0 & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta $} t}/2 & \text{$\Omega_1/2
			$} & \text{$\alpha$}-2 \text{$\Delta_2$}- \text{$\Delta_1$} \\
	}
	\end{equation}
\end{widetext}
Here , $\delta = \omega_{dr}^1 - \omega_{dr}^2$.

Finally, in \autoref{fig:main_scheme}

Let's consider the Hamiltonian (\autoref{matrix}) in details. Divide it into three parts: time-dependent $(V_t)$, the part responsible for the interaction between the qubits $(V_J)$ and all the rest $(H_0)$.
\begin{equation}
	H^R=H_0+V_J+V_t
\end{equation}
The $\Omega_1\gg \Omega_2,\Delta_2> J$, so the driven field on the first qubit is strong and form the dressed states defined by the Hamiltonian $H_0$, which is stationary, so the levels can be found and schematically depicted in \autoref{fig:main_scheme}~(b). The drive on the second qubit is weak with very low intensity, so we can neglect any perturbation introduced by second drive on the position, width of the dressed states.
At our working point the condition $\Delta_2=\alpha/2$ is met and $H_0$ becomes degenerate.

According to the degenerate perturbation theory (with perturbation $V_J$) we found the first-order corrections to the wave functions. Calculating the probability of two-photon transition per unit interaction time using the \autoref{prob} for corrected  wave functions and neglecting small terms we obtain:
\begin{equation}
	A^{(2)}_{1\rightarrow 6} =\frac{\pi\Omega_2^4}{8} \frac{8 J^4 (6 \text{$\alpha $}+19 \text{$\Omega_1 $})^2}{\text{$\alpha
			$}^6 \text{$\Omega_1$}^2}
\end{equation}
\begin{equation}
A^{(2)}_{2\rightarrow 5} =\frac{\pi\Omega_2^4}{8} \frac{8 J^4 (6 \text{$\alpha $}-19 \text{$\Omega_1 $})^2}{\text{$\alpha
		$}^6 \text{$\Omega_1$}^2}
\end{equation}

So, in the system of non-interacting qubits $(J=0)$ some transitions are prohibited and the splitting we are interested in is not observed. Therefore a non-zero interaction between qubits is necessary to observe AT effect in our system.

@@

\begin{figure}
	\includegraphics[width=\linewidth]{intro_scheme}
	\caption{Illustrating the A-T splitting by  the classical driving in the rotating frame ($\hbar=1$ here). \textbf{(a)} The three-level system is driven strongly by a ``coupler'' tone of amplitude $\Omega$ at frequency $\omega_{01}-\Delta$. It induces Rabi oscillations between $\ket{0}$ and $\ket{1}$ at the generalized Rabi frequency $\Omega_R = \sqrt{\Omega^2 + \Delta^2}$. \textbf{(b)} Moving to the frame rotating with the drive, we effectively change the $\ket{0}\rightarrow \ket{1}$ transition frequency to $\Delta$. However, when RWA is applied and Hamiltonian is re-diagonalized, the splitting between two lowest levels (dressed states $\ket{a}$ and $\ket{b}$) becomes $\Omega^R$. Now, the experimenter may observe a doublet transition from these levels to the state $\ket{2}$ at frequencies $\omega_{12}+(\Delta \pm \Omega^R)/2$.} 
	\label{fig:at-standard}
\end{figure}

@@

\section{Degenerate perturbation theory}
\begin{equation}
H^R=H_0+V_J
\end{equation}
At our working point the equation $\Delta_2=\alpha/2$ is true and $H_0$ becomes degenerate. Let's consider our system in the basis of dressed states.
\begin{equation}
H_0^{d}= diag(-\frac{\Omega_{1}}{2},\frac{\Omega_{1}}{2},\frac{(-\alpha-\Omega_{1})}{2},\frac{-\alpha+\Omega_{1}}{2},-\frac{\Omega_{1}}{2},\frac{\Omega_{1}}{2})
\end{equation}
The choice of wave functions from a degenerate subspace is arbitrary because any linear combination of functions from this subspace will satisfy the Schrodinger equation. However, if we demand that the change of wave functions be small under the applied small perturbation, then the choice of wave functions become defined. To obtain correct wave functions we need to diagonalize $V_J^{d}$ in the degenerate subspace. However, we can notice that $V_J^{d}$ is identically the zero matrix in our subspace, so technically any choice of basis will diagonalize $V_J^{d}$. This means that the degeneracy is not lifted at first-order in perturbation theory. We have to pick eigenvectors which diagonalize following matrix:
\begin{equation}
	\begin{matrix}
	M_{nn'} = \sum_{m}\frac{V_{nm}V_{mn'}}{E_n-E_m}
	\end{matrix}
\end{equation}
Where $\ket{n}$ and $\ket{n'}$ are states with same energy $E_n$.  The sum is over all states $m$ not in the degenerate subspace.
For example, in our case for one of degenerate subspaces:
\begin{equation}
	M_{15} =\left[\begin{matrix}\frac{J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)} & \frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)}\\\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)} & \frac{2 J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)}\end{matrix}\right]
\end{equation}
The normalized eigenvectors $(C_n,C_{n'})$ of the matrix will give the desired zero approximation wave-functions.
The first-order correction to the states from degenerate subspace:
\begin{equation}
	\ket{n^0}+\ket{n^1} = \sum_n C_{n}\ket{n^0} + \sum_{m\ne n}\ket{m^0}\frac{\bra{m^0}V\ket{n^0}}{E_n^0-E_m^0}
\end{equation}
The sum is over all states $n$ in the degenerate subspace $n=(n,n')$.
The first-order corrections for not degenerate state compute by using the ordinary perturbation theory.
\begin{equation}
	\ket{j^1} = \sum_{m\ne j}\ket{m^0}\frac{\bra{m^0}V\ket{j^0}}{E_j^0-E_m^0}
\end{equation}

\section{Theoretical description of two-photon process}
Perturbation theory allows semianalytical calculation of the transition rates for single and multi-photon processes\cite{faisal2013theory}.

>>>>

Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr1}+\hat H_{tr2}+\hat H_{dr1}+\hat H_{dr2}+\hat H_{int},
\end{equation}
where $\hat H_{int} = J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms. In the following, we will also transform \eqref{eq:master} into the frame rotating with both drives by an operator
\begin{align}
&\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\label{eq:R}\\
&\hat H_R = \hat R^{\dagger}\hat H \hat R - i\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
\end{align}
After the transformation and application of the RWA:
\begin{equation}
\begin{aligned}
	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{-(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{(\omega_d^1 - \omega_d^2)t}\right],\\
	\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{dr}^2 \rightarrow \frac{\Omega_2}{2}(\hat c  + \hat c^\dag).
\end{aligned}
\label{eq:RWA}
\end{equation}

@@

Remarkably, in areas I, II and III we could observe avoided crossings and triplet transitions which turn out to be impossible to explain using only the stationary Hamiltonian without driving terms. We confirm this by numerically diagonalizing $\hat H_{tr1}+\hat H_{tr2}+\hat H_{int}$ taking 3 levels for each transmon (and total 9 basis states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:statinary_levels} in Appendix. While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}, it completely misses the Roman-numbered effects. Taking into account more energy levels for transmons does not help, and is not even necessary to reproduce the experiment, as we will show in the following.

@@

\paragraph{Features I, II and III.} First, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the transmon 2. Upon this, it has become clear that feature II and feature III actually are of the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition from $\ket{00}$ to $\ket{01}$ intersects with the two-photon one $\ket{20/2}$ ($\ket{10}$ intersects $\ket{02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b).

From \autoref{fig:statinary_levels} we conclude that avoided crossing in III is between two transitions: $\ket{00}\rightarrow\ket{12/3}$ and $\ket{10}\rightarrow \ket{02}$ which are of the same frequency when $\omega_1 = \omega_2-\alpha_2/2$. The latter process is discernible in \autoref{fig:statinary_levels} as it depopulates $\ket{10}$, but is not visible in \autoref{fig:two-tone}. From additional simulations, we have found that the size of the splitting depends on the driving power on the first transmon; the results are shown in \autoref{fig:zoom}. There is no dependence on the drive power on the second transmon, though. As one can see, the growth of the splitting with increasing power is approximately linear: its width is roughly equal to the FWHM of the $\ket{10}$ spectral line which is approximately $\Omega_1/2\pi$ Hz.

@@

These observation lead to understanding that the effect is caused by light dressing. In the case III, the first transmon is dressed by a strong resonant field; in case II, the second one; finally, in case I, both transmons are dressed at the same time. We will discuss these effects in greater detail in \autoref{sec:theory}.

@@

\begin{figure*}
	\centering
	\includegraphics[width=.9\linewidth]{main_scheme}
	\caption{Explaining the origin of the AT satellites for feature III. \textbf{(a)} System level structure at 3.65 mA. At this current, the first transmon (orange) is below the second one (blue) exactly by $\alpha_2/2$. The first transmon is driven by a strong signal of amplitude $\Omega_1$ at a small detuning $\Delta_1$ from $\omega_1$ shown in green. The transmon-transmon interaction in RWA conserves the number of excitations and is depicted as orange-blue circles. \textbf{(b)} Moving to the frame rotating with the drive of the first transmon, we make all the states $\ket{0j},\ket{1j}$ nearly degenerate (in fact, now the first transmon splitting equals $\Delta_1$). However, the presence of a strong excitation lifts the degeneracy and the splitting changes to $\Omega_1^R = (\Omega_1^2 + \Delta_1^2)^{\frac{1}{2}}$ (the first transmon becomes light-dressed). \textbf{(c)} Transitions in the light-dressed system when the second qubit is excited (level subspaces coupled by $\hat H_{dr}^2$ are shown with blue ellipses). In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted: the green transitions are not shifted in frequency, the red are red-shifted by $\Omega^R_1/2$ and the blue are blue-shifted by $\Omega^R_1/2$. In the right part, the most contributing trajectories are depicted; red crosses show transitions that are forbidden without the coupling $J$.}
	\label{fig:main_scheme}
\end{figure*}

@@

Since we had already connected the additional avoided crossings with light dressing, it was natural to expect the Autler-Townes effect to cause them. For a three-level system, the standard A-T effect is reviewed in Appendix \ref{sec:3-level-at}. However, in our case the situation is more complicated. We will first explain the feature III.

First of all, since during the spectroscopy we apply only a single microwave tone, it has to be simultaneously the coupler tone and the probe tone to observe the A-T effect. This is possible due to the resonance condition $\omega_1 = \omega_2+\alpha_2/2$ at III which means that we can simultaneously excite transitions $\ket{10}$ and $\ket{02/2}$. Since the two-photon Rabi frequency is much smaller than the single-photon $\Omega_2$, it is natural to view this two-photon excitation as the probing process which does not affect the level structure. In contrast, the single-photon excitation is enough to dress the system. In other words, in our case the A-T coupling operator is $\hat H_{dr}^1$ (strong), and the probing operator is $\hat H_{dr}^2$ (weak in the two-photon regime). Their separation in our case is not in frequency but in the Hilbert subspaces they act upon.

In \autoref{fig:main_scheme}, we elaborate on how exactly the A-T effect occurs for feature III. \autoref{fig:main_scheme}~(a) demonstrates the unmodified level structure of the SAM. Since from numerical simulations we know that level $\ket{02}$ is not necessary to observe the splitting, it is only shown with a dashed line, and hereinafter we consider the first transmon as a two-level system.

The next step is to view the system in the frame rotating with the first transmon (\autoref{fig:main_scheme}~(b)) and then move to the  dressed picture similarly to Appendix \ref{sec:3-level-at}. Now, the first transmon splitting equals $\Omega_{1}^R = \sqrt{\Omega_1^2+\Delta_1^2}$, and its the new eigenstates (dressed states) are denoted $\ket{a}$ and $\ket{b}$. At the same time, the second transmon energies stay the same.

Finally, in \autoref{fig:main_scheme}~(c) we demonstrate possible two-photon transitions between the resulting eigenstates due to $\hat H_{dr}^2$. In the left part of the panel, the unmodified transition at $\omega_1$ and two sidebands at $\omega_1 \pm \Omega_1^R/2$. The right part describes the mechanism of these two-photon processes through virtual excitations of the intermediate states. From here it becomes obvious that without the transmon-transmon interaction the sideband transitions are forbidden due the selection rule: $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2 \ket{b, j+1} = 0$ since $\braket{a}{b} = 0$. However, we will show that they become allowed in the second order in $J$ when the coupling is turned on.  Remarkably, due to the two-photon nature of the transitions, the Autler-Townes splitting in this case will be just $\Omega_1^R$.

Now, we will repeat this reasoning in a quantitative mathematical model. We start from the initial Hamiltonian \eqref{Hsystem}. To move to the rotating frame with \eqref{eq:rotation} and apply the RWA, will use the following operator:
\begin{equation}
R = \exp[-i\omega_d^1 t (b^{\dagger}b+c^{\dagger}c)]
\end{equation}  
Note that we rotate both transmon subspaces simultaneously in contrast to what is shown in \autoref{fig:main_scheme} because below it will be convenient to have time-independent $\hat H_{int}$:
\begin{equation}
\begin{aligned}
\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{1},\\
\hat H_{int} &\rightarrow J \left[\hat \sigma_+ \hat c + \hat \sigma_-\hat c^\dag \right],\\
\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2} \hat \sigma_x,\ 
\hat H_{dr}^2 \rightarrow \frac{\Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
\end{aligned}
\end{equation}
where $\delta = \omega_{dr}^2 - \omega_{dr}^1$.

Since $\hat H_{dr}^1$ is now time-independent, we can move to the dressed basis by applying a transformation $\hat S$ which diagonalizes the first transmon. After that, the Hamiltonian may be split into three parts:
\begin{equation}
\begin{aligned}
\hat H^{D} &= \left[\frac{\Delta_1}{2} \hat{\mathbbm{1}}+\frac{\Omega_1^R}{2}\hat \sigma_z\right] + \Delta_2 \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),\\
\hat V_J &= \hat S^\dag \hat H_{int}\hat S,\\
\hat V_t &= \hat S^\dag \hat H_{dr}^{2} \hat S \equiv \hat H_{dr}^{2}.
\end{aligned}
\end{equation}
The first part is diagonal, and the remaining two will be treated as perturbations. To simplify futher calculations, we take the working point where $\Delta_1 = 0$ and $\Delta_2= - \alpha/2$. In these conditions, $H^D$ becomes degenerate as can be seen below in \eqref{eq:ham_matrix}:

 \renewcommand{\kbldelim}{[}% Left delimiter
\renewcommand{\kbrdelim}{]}% Right delimiter
\begin{widetext}
	\begin{equation}
	\hat H^D + \hat V_J + \hat V_t  = \kbordermatrix{
		&\ket{a,0} & \ket{b,0} & \ket{a,1} & \ket{b,1} & \ket{a,2} & \ket{b,2} \\
		\ket{a,0}& -\frac{\Omega_1}{2} & 0 & \frac{\Omega_{2}e^{i \text{$\delta$} t}}{2} -\frac{J}{2} & \frac{J}{2} & 0 & 0 \\
		\ket{b,0} & 0 & \frac{\Omega_1}{2} & -\frac{J}{2} & \frac{\Omega_2 e^{i \delta t}}{2} + \frac{J}{2} & 0 & 0 \\
		\ket{a,1} &\frac{\Omega_2 e^{-i \text{$\delta$} t} }{2}  - \frac{J}{2} & -\frac{J}{2} & - \frac{\alpha}{2} - \frac{\Omega_1}{2}&
		0 & \frac{\text{$\Omega_2$} e^{i \text{$\delta$} t}}{\sqrt{2}} -\frac{J}{\sqrt2} & \frac{J}{\sqrt2} \\
		\ket{b,1} & \frac{J}{2} & \frac{\text{$\Omega_2$} e^{-i \text{$\delta $} t}}{2} +\frac{J}{2} & 0 & - \frac{\alpha}{2} + \frac{\Omega_1}{2} & -\frac{J}{\sqrt 2} & \frac{\text{$\Omega_2$} e^{i \text{$\delta
					$} t}}{\sqrt 2} + \frac{J}{\sqrt 2} \\
		\ket{a,2} & 0 & 0 & \frac{\Omega_2 e^{-i \delta t}}{2} - \frac{J}{\sqrt 2} & -\frac{J}{\sqrt 2} &
		-\frac{\Omega_{1}}{2} & 0 \\
		\ket{b,2} & 0 & 0 & \frac{J}{\sqrt 2} & \frac{\text{$\Omega_2$} e^{-i \text{$\delta $} t}}{\sqrt 2} + \frac{J}{\sqrt 2} & 0 & \frac{\Omega_{1}}{2}\\
	}
	\label{eq:ham_matrix}
	\end{equation}
\end{widetext}

Using the degenerate perturbation theory with $\hat V_J$ summarized in Appendix \ref{sec:dpt}, we have found the first-order corrected wave functions of $\hat H^D$, labelled $\ket{k},\ k=1..6$.

The theory for two-photon processes is given in Appendix \ref{sec:2pp}. The probability rate of two-photon transition per unit interaction time using corrected eigenstates $\ket{k}$ and neglecting small terms we obtain:
\begin{equation}
	A^{(2)}_{1\rightarrow 6} =\frac{\pi\Omega_2^4}{8} \frac{8 J^4 (6 \text{$\alpha $}+19 \text{$\Omega_1 $})^2}{\text{$\alpha
			$}^6 \text{$\Omega_1$}^2}
\end{equation}
\begin{equation}
A^{(2)}_{2\rightarrow 5} =\frac{\pi\Omega_2^4}{8} \frac{8 J^4 (6 \text{$\alpha $}-19 \text{$\Omega_1 $})^2}{\text{$\alpha
		$}^6 \text{$\Omega_1$}^2}
\end{equation}

From here it follows that in the studied SAM the sideband transitions are prohibited without interaction $(J=0)$ even in the second order, and the avoided crossing we are interested can not be observed.

@@

\begin{figure}
	\includegraphics[width=.9\linewidth]{intro_scheme}
	\caption{Illustrating the A-T splitting by  the classical driving in the rotating frame ($\hbar=1$ here). \textbf{(a)} The three-level system is driven strongly by a ``coupler'' tone of amplitude $\Omega$ at frequency $\omega_{01}-\Delta$. It induces Rabi oscillations between $\ket{0}$ and $\ket{1}$ at the generalized Rabi frequency $\Omega_R = \sqrt{\Omega^2 + \Delta^2}$. \textbf{(b)} Moving to the frame rotating with the drive, we effectively change the $\ket{0}\rightarrow \ket{1}$ transition frequency to $\Delta$. However, when RWA is applied and Hamiltonian is re-diagonalized, the splitting between two lowest levels (dressed states $\ket{a}$ and $\ket{b}$) becomes $\Omega^R$. Now, the experimenter may observe a doublet transition from these levels to the state $\ket{2}$ at frequencies $\omega_{12}+(\Delta \pm \Omega^R)/2$.} 
	\label{fig:at-standard}
\end{figure}

@@

\section{Degenerate perturbation theory} \label{sec:dpt}
\begin{equation}
H^R=H_0+V_J
\end{equation}
At our working point the equation $\Delta_2=\alpha/2$ is true and $H_0$ becomes degenerate. Let's consider our system in the basis of dressed states.
\begin{equation}
H_0^{d}= diag(-\frac{\Omega_{1}}{2},\frac{\Omega_{1}}{2},\frac{(-\alpha-\Omega_{1})}{2},\frac{-\alpha+\Omega_{1}}{2},-\frac{\Omega_{1}}{2},\frac{\Omega_{1}}{2})
\end{equation}
The choice of wave functions from a degenerate subspace is arbitrary because any linear combination of functions from this subspace will satisfy the Schrodinger equation. However, if we demand that the change of wave functions be small under the applied small perturbation, then the choice of wave functions become defined. To obtain correct wave functions we need to diagonalize $V_J^{d}$ in the degenerate subspace. However, we can notice that $V_J^{d}$ is identically the zero matrix in our subspace, so technically any choice of basis will diagonalize $V_J^{d}$. This means that the degeneracy is not lifted at first-order in perturbation theory. We have to pick eigenvectors which diagonalize following matrix:
\begin{equation}
	\begin{matrix}
	M_{nn'} = \sum_{m}\frac{V_{nm}V_{mn'}}{E_n-E_m}
	\end{matrix}
\end{equation}
Where $\ket{n}$ and $\ket{n'}$ are states with same energy $E_n$.  The sum is over all states $m$ not in the degenerate subspace.
For example, in our case for one of degenerate subspaces:
\begin{equation}
	M_{15} =\left[\begin{matrix}\frac{J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)} & \frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)}\\\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)} & \frac{2 J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)}\end{matrix}\right]
\end{equation}
The normalized eigenvectors $(C_n,C_{n'})$ of the matrix will give the desired zero approximation wave-functions.
The first-order correction to the states from degenerate subspace:
\begin{equation}
	\ket{n^0}+\ket{n^1} = \sum_n C_{n}\ket{n^0} + \sum_{m\ne n}\ket{m^0}\frac{\bra{m^0}V\ket{n^0}}{E_n^0-E_m^0}
\end{equation}
The sum is over all states $n$ in the degenerate subspace $n=(n,n')$.
The first-order corrections for not degenerate state compute by using the ordinary perturbation theory.
\begin{equation}
	\ket{j^1} = \sum_{m\ne j}\ket{m^0}\frac{\bra{m^0}V\ket{j^0}}{E_j^0-E_m^0}
\end{equation}

\section{Theoretical description of two-photon process}\label{sec:2pp}
Perturbation theory allows semianalytical calculation of the transition rates for single and multi-photon processes\cite{faisal2013theory}.
